A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-14 paper.tex
Added 'many' citations

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations} \chris{I'm not sure what you want to cite here.} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.

>>>>

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}. In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
